Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
489 - 672 done

-   Aditya (169027493)
-   Andy
-   Dibu
-   Oscar
-   Taras

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE)
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )

@@

```{r covid_2020, error=TRUE}
# YOUR CODE HERE

@@

```{r covid_2020_parquet, error=TRUE}
# YOUR CODE HERE
```

@@

```{r aware_fixed_country, error=TRUE}
aware_fixed_country <- climate_awareness |>
    mutate(
        # Replace *all* *literal* periods with a space in the country column
        # YOUR CODE HERE
    )

@@

```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
        # Change country using a case_when statement
        # YOUR CODE HERE
    )

@@

```{r aware_pop, error=TRUE}
# YOUR CODE HERE

@@

```{r covid_2020_match_country, error=TRUE}
# YOUR CODE HERE

>>>>

-   Aditya (169027493)
-   Andy
-   Dibu (169708451)
-   Oscar
-   Taras

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE

@@

```{r covid_2020, error=TRUE}
covid_2020 <- covid_cases |>
  filter(year(date) == 2020) |>
  group_by(location, continent) |>
  summarise(
    total_cases = sum(total_cases)
  ) |>
  rename(country = location)

@@

```{r covid_2020_parquet, error=TRUE}
write_parquet(covid_2020, "covid_2020.parquet")
```

@@

```{r aware_fixed_country, error=TRUE}
aware_fixed_country <- climate_awareness |>
    mutate(
        # Replace *all* *literal* periods with a space in the country column
        country = str_replace_all(country, "\\.", " ")
    )

@@

```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
      # Change country using a case_when statement
      country = case_when(
        country == "Bolivia (Plurinational State of)" ~ "Bolivia",
        country == "Congo (Democratic Republic of the)" ~ "Congo, Rep.",
        country == "Egypt" ~ "Egypt, Arab Rep.",
        country == "Hong Kong" ~ "Hong Kong SAR, China",
        country == "Lao People's Democratic Republic" ~ "Lao PDR",
        country == "Slovakia" ~ "Slovak Republic",
        country == "North MAcedonia" ~ "North Macedonia",
        country == "South Korea" ~ "Korea, Rep.",
        country == "Turkey" ~ "Turkiye",
        country == "Vietnam" ~ "Viet Nam",
        country == "Yemen" ~ "Yemen, Rep.",
        TRUE ~ country
      )
    )

@@

```{r aware_pop, error=TRUE}

aware_pop <- full_join(
  aware_fixed_country,
  pop_data,
  by = "country"
) |> full_join(population) |>
  group_by(country, aware_no, aware_alittle, aware_moderate, aware_alot, aware_refuse) |>
  summarise(total_population = sum(population))

@@

```{r covid_2020_match_country, error=TRUE}
covid_2020_match_country <- left_join(aware_pop, covid_2020, by = "country")
